ANNO: The Anthropological Notation Ontology

### 2023-03-29 paper.tex
Fix aw macro usage.

\begin{abstract}
Anthropology relies on osteometric measurements of human bones, but ...
In this paper, first, we describe the anthropology domain.
Then, we discuss design decisions of modelling ANNO.
Next, we show how ANNO is published for the community.
Finally, we describe the integration of the ontology into \aw.
\end{abstract}

@@

TODO: Modellierung der Anthropologie-Domäne (u.a. Motivation, related work, was ist neu).
TODO: Dann könnte man Design-Entscheidungen beschreiben (wie und warum wurden bestimmte Sachverhalte so in der Ontologie modelliert).
\section{Publication}
ANNO is published on \url{https://ols.imise.uni-leipzig.de} as well as \url{https://annosaxfdm.de/ontology/}.
TODO: Bereitstellung der Ontologie für die Community (OLS etc.). 
\section{Integration into \aw}
TODO: Integration der Ontologie in die Anwendung.
%\subsection{}\label{s1.1}

\section{Conclusion and Future Work}
% Basiert auf dem Fazit aus dem Projektbericht
ANNO introduces uniform definitions for the anatomical landmarks of the human skeletal system as well as osteometric landmarks, measurement distances and functions.
The ontology is interlinked with ... and includes sources for all external definitions.
The ontology is used in \aw in place of an old, hard-coded format, which saves development time, separates annotation file compatibility from software versions, eases annotation through hierarchical browsing and increases interoperability.
% following two sentences are machine translated, improve and rewrite
It provides a basis for future training of ontologists, knowledge managers, further research activities and specialization opportunities in this field.
Furthermore, there is interest of the results in forensic, historical and prehistoric anthropology, pathology and medicine as well as in the field of computer science and especially medical informatics.
%Moreover, the ontology can be extended.

>>>>

\begin{abstract}
Anthropology relies on osteometric measurements of human bones, but ...
In this paper, first, we describe the anthropology domain.
Then, we discuss design decisions of modelling ANNO.
Next, we show how ANNO is published for the community.
Finally, we describe the integration of the ontology into \aw{}.
\end{abstract}

@@

TODO: Modellierung der Anthropologie-Domäne (u.a. Motivation, related work, was ist neu).
TODO: Dann könnte man Design-Entscheidungen beschreiben (wie und warum wurden bestimmte Sachverhalte so in der Ontologie modelliert).
\section{Publication}
ANNO is published on \url{https://ols.imise.uni-leipzig.de} as well as \url{https://annosaxfdm.de/ontology/}.
TODO: Bereitstellung der Ontologie für die Community (OLS etc.). 
\section{Integration into \aw{}}
TODO: Integration der Ontologie in die Anwendung.
%\subsection{}\label{s1.1}

\section{Conclusion and Future Work}
% Basiert auf dem Fazit aus dem Projektbericht
ANNO introduces uniform definitions for the anatomical landmarks of the human skeletal system as well as osteometric landmarks, measurement distances and functions.
The ontology is interlinked with ... and includes sources for all external definitions.
The ontology is used in \aw{} in place of an old, hard-coded format, which saves development time, separates annotation file compatibility from software versions, eases annotation through hierarchical browsing and increases interoperability.
% following two sentences are machine translated, improve and rewrite
It provides a basis for future training of ontologists, knowledge managers, further research activities and specialization opportunities in this field.
Furthermore, there is interest of the results in forensic, historical and prehistoric anthropology, pathology and medicine as well as in the field of computer science and especially medical informatics.
%Moreover, the ontology can be extended.
